Clustering exploration for `r params$library_id`

### 2024-08-05 analyses/cell-type-ewings/template_notebooks/auc-singler-workflow/03-clustering.Rmd
add comments and document

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: "SCPCL000822"
  sce_file: "../../../../data/current/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  singler_results_file: "../../results/aucell_singler_annotation/SCPCS000490/SCPCL000822_singler-classifications.tsv"
  cluster_results_file: "../../results/aucell_singler_annotation/SCPCS000490/SCPCL000822_clusters.tsv" 
  marker_genes_file: "../../references/visser-all-marker-genes.tsv"
---

@@

- Louvain clusters are calculated using a range of parameters specifying nearest neighbors (5, 10, 15, 20, 25, 30, 35, and 40). 
- Metrics are then calculated to evaluate clustering results across all parameters: 
  - Silhouette width 
  - Cluster purity 
  - Cluster stability 
- The clusters are then compared to the results from running `SingleR` in the `aucell-singler-annotation.sh` workflow.
- We then look at marker gene expression across the clusters and assign each cluster to a cell type.

@@

```{r}
# calculate cluster stability
stability_df <- get_cluster_stability(sce, all_cluster_results) |>
  dplyr::mutate(
    k_value = as.factor(k_value),
    # make sure that k = 5 comes first
    k_value = forcats::fct_relevel(k_value, "5", after = 0)
  )

@@

For the plots, we will only display the top 7 cell types and all other cells will be lumped together into `All remaining cell types`.

@@

We will also look at the expression of marker genes across each cluster. 
In these plots, each row shows the distribution of the specified marker genes in that cluster. 
Each panel is labeled with the marker gene expression being plotted.

>>>>

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  singler_results_file: NULL
  cluster_results_file: NULL
  marker_genes_file: NULL
---

@@

- Louvain, Jaccard clusters are calculated using a range of parameters specifying nearest neighbors (5, 10, 15, 20, 25, 30, 35, and 40). 
- Metrics are then calculated to evaluate clustering results across all parameters: 
  - Silhouette width 
  - Cluster purity 
  - Cluster stability 
- The clusters are then compared to the results from running `SingleR` in the `aucell-singler-annotation.sh` workflow.
- We then look at marker gene expression across the clusters and assign each cluster to a cell type.

@@

```{r, warning=FALSE, message=FALSE}
# calculate cluster stability
stability_df <- get_cluster_stability(sce, all_cluster_results) |>
  dplyr::mutate(
    k_value = as.factor(k_value),
    # make sure that k = 5 comes first
    k_value = forcats::fct_relevel(k_value, "5", after = 0)
  )

@@

For the plots, we will only display the top 7 cell types identified by `SingleR` and all other cells will be lumped together into `All remaining cell types`.

@@

Finally, we will look at the expression of marker genes across each cluster for each value of K. 
In these plots, each row shows the distribution of the specified marker genes in that cluster. 
Each panel is labeled with the marker gene expression being plotted.
